---
title: "integral"
author: "casi"
date: "April 7, 2015"
output: html_document
---

```{r}
library('ggplot2')
library('pracma')

```
A. Function that calculates integrals with the rejection sampling method. 
First, we will build up a function in R which takes as parameters the number of points into our phase space,the function we want to integrate,and both maximun and miminum values into our integration domain. Moreover, the function we want to integrate must be smooth and positive all over the integration domain.

```{r}
integrar <- function(n,f, x_min, x_max)
{  
  #Starting we need two vectors which represent 10000 evenly spaced numbers, ready to be filled up in next steps. One for x, the independent variable, and onde for y which depends on 
  #x. Right after, we take the maximun and minimum numbers and save them into variables. This is because they will define our phase space of random points. In addition, we take
  #just the random points that seem to be useful for our function (that means they must be inside the interval from the min to the max value, below the function). 
  xvec <- linspace(x_min, x_max,  10000)   
  yvec <- f(xvec)
  y_max <- max(yvec)   
  y_min <- min(yvec)
  x_random <- runif(n, x_min, x_max)
  y_random <- runif(n, y_min, y_max)
  #We had saved this points, the ones capable of represent the function we want to integrate. To see how this process occurs, we had made some simple graphs to show it. 
  
  #The first one shows the line function we want to integrate.
  data1 <- data.frame(xvec, yvec)
  plot1 <- ggplot(data1, aes(x=xvec,y=yvec)) + ggtitle('Function to integrate') + geom_line(colour = 'blue')   
  print(plot1) 
  
  #Second one shows the final reconstruction of the function integral with this method of sampling rejection.
  #We choose only the points that lie below the function, these are the ones we plot. 
  
  delta <- f(x_random) - y_random
  under <- which(delta>0.0) #es como la funcion where en python, un boolean para evitar hacer un for.
  a <- x_random[under]
  b <- y_random[under]
  data2 <- data.frame(a, b)
  plot3 <- ggplot(data2, aes(a,b)) + ggtitle('Calculated integral') + geom_point(colour = 'green')
  print(plot3)
  
  #Finally, we get to calculate the numerical result. If we recall the integral as a huge sum over tiny columns along the function curve, we can calculate the area for each one
  #taking the lenght as the y coordinate and the width as the x coordinate and, of course, these will be the interval between the max and min values in each case. 
  columna_int <- (x_max-x_min)*(y_max-y_min)
  integral = columna_int*(size(under)/(1.0*size(y_random)))  #bota un warning pero no se por que
  return (integral)
  
  #The total value of the integral will be the total number of points under the curve within the total area, calculated above
  
}
```


B. Calculate cos(50*x)+sin(20*x))^2 in [0,1]
Using our function, and calling c the function we want to integrate

```{r}
c <- function(x)
{
  return((cos(50*x)+sin(20*x))^2)   
}

print(integrar(10000,c,0,1)) # U[0.1]

#Now comparing with the r-function Integrate
integrar2<- function(x) {
  integrate(c,lower=0, upper=1)
}

print(integrar2(c))

#We see that the values of both process are very alike and still inside the absolute value.

```

```{r}
c <- function(x)
{
  return((cos(50*x)+sin(20*x))^2)   
}

print(integrar(10000,c,0,1)) # U[0.1]

#Now comparing with the r-function Integrate
integrar2<- function(x) {
  integrate(c,lower=0, upper=1)
}

print(integrar2(c))

#We see that the values of both process are very alike and still inside the absolute value.

```

C. Calculate 1/((1 + x^2)xpi) in [2,inf]. At first sight, this integral looks extremely complicated, nevertheless, with some research we had discovered the easiest way to solve it: Change of variable. For this we decided to write y=1/x, therefore our new function is x^(-2)/(pix(1+x^(-2))), and replacing in the limits we get our new integration interval as [0, 1/2]

```{r}
d <- function(x)
{
  return(x^(-2)/(pi*(1+x^(-2))))   
}

print(integrar(10000,d, 0.01, 0.5))
```
In this case, we see an important difference between the values obtained through the methods, but still in approximation correspond to close values, taking into account the absolute value calculated.